# cachemeR

[![Build Status](https://travis-ci.org/Tazovsky/cachemeR.svg?branch=devel)](https://travis-ci.org/Tazovsky/cachemeR)
[![codecov](https://codecov.io/gh/Tazovsky/cachemeR/branch/devel/graph/badge.svg)](https://codecov.io/gh/Tazovsky/cachemeR)
[![Coverage Status](https://coveralls.io/repos/github/Tazovsky/cachemeR/badge.svg?branch=devel)](https://coveralls.io/github/Tazovsky/cachemeR?branch=devel)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ">"
)
```

## Overview {#overview}

`cachemeR` is a convenient way of caching objects in R. 
From the beginning the purpose of this package is to make caching as easy as possible 
and to put as less effort as possible to implement it in existsing projects :)

## Installation {#installation}


```{r eval=FALSE}
if (!require("devtools")) 
  install.packages("devtools")

devtools::install_github("Tazovsky/cachemeR@devel")
```

## Usage - `%c-%` operator {#usage}

Cache has to be initialized. It requires to run `cachemer$new` with path to `config.yaml`. 
Then all you need to cache is to use pipe **`%c-%`** instead of assignment operator `<-`. 
In following example function `doLm` fits linear model:

```{r}
library(cachemeR)

doLm <- function(rows, cols) {
  print("Function is run")
  set.seed(1234)
  X <- matrix(rnorm(rows*cols), rows, cols)
  b <- sample(1:cols, cols)
  y <- runif(1) + X %*% b + rnorm(rows)
  model <- lm(y ~ X)
}

# create dir where cache will be stored
dir.create(tmp.dir <- tempfile())

# create path to config.yaml - yaml fild must be in that dir
config.file <- file.path(tmp.dir, "config.yaml")

# initialize cachemeR
cache <- cachemer$new(path = config.file)

cache$setLogger(TRUE)

# cache function
result1 %c-% doLm(5, 5)
result1

# function is cached now so if you re-run function then 
# output will be retrieved from cache instead of executing 'doLm' function again
result2 %c-% doLm(5, 5)
result2

```

```{r, include=FALSE}
on.exit(unlink(dirname(config.file), T, T))
```

Operator `%c-%` is sesitive to function name, function body, argument (whether argument is named or not, 
or is list or not, or is declared in parent environment, etc.). But it also **has some [limitations](#limitations)**.

## Use cases {#usecases}

## Limitations {#limitations}

- $ in argument
- res %c-% fun(a = 1, b =2) + 1
- res %c-% (fun(a = 1, b =2) + 1)
- doesn't work with piepi `%>%` 

## Microbenchmark {#microbenchmark}

calc fibonacci

```{r}

# fib5 <- calculateFibonacci(5)
# fib5 %c-% calculateFibonacci(5)

```

