---
title: "Save nad restore cache"
author: "Kamil Foltyński"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ">"
)
```

## How caching works in `cachemeR` package

Cached objects are stored in provided location as `.rds`:

```{r}
library(cachemeR)

# create cache location
dir.create(cache.dir <- tempfile())
config.file <- file.path(cache.dir, "config.yaml")
print(config.file)
cache <- cachemer$new(path = config.file)

cache$setLogger(TRUE)

start.t <- Sys.time()
res1 %c-% testFun(1:23, b = 1, list(d = 2, e = 3))
res2 %c-% testFun(1:50, b = 2, list(d = 4, e = 5))
lm_fit %c-% doLm(500, 500)
t1 <- Sys.time() - start.t
t1

# list cached objects:
list.files(cache.dir)

cache$clear()

```

After you restart `R` session, run `cache$clear()` or clear environment you can easily restore cached objects 
by providing path to `config.yaml`:

```{r}
# only path to config.yaml is needed to restore cached objects
# t1 is for time comparison
rm(list = ls()[!ls() %in% c("config.file", "t1")])

library(cachemeR)

print(config.file)

# list cached objects:
list.files(dirname(config.file))

cache <- cachemer$new(path = config.file)

start.t <- Sys.time()
res1 %c-% testFun(1:23, b = 1, list(d = 2, e = 3))
res2 %c-% testFun(1:50, b = 2, list(d = 4, e = 5))
lm_fit %c-% doLm(500, 500)
t2 <- Sys.time() - start.t
t2


```

```{r, include=FALSE}
on.exit(unlink(dirname(config.file), T, T))
```


The first execution of the code lasted **`r round(t1, 4)`** sec(s). 

The second execution was from cache and took **`r round(t2, 4)`** sec(s) only. 

You saved **`r round(t1 - t2, 4)`** sec(s) of your time! :)



